### 2023-10-26 paper.tex
Added LaTeX Paper
Added the LaTeX final paper for the project.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Graphical Databases for IoT Device Management and Anomoly Detection}

\author{\IEEEauthorblockN{Colter Snyder}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Colorado School of Mines}\\
Golden, Colorado, USA \\
csnyder1@mines.edu}
}

\maketitle

\begin{abstract}
IoT devices have exploded in use over the past few years.
This has caused concerns over data privacy and security.
Many papers have been writen to detect IoT devices and catalog them,
however none use a graphical database in order to do so.
Using a graphical database provides many benefits over current systems
and allows for new questions to be answered.
\end{abstract}

\begin{IEEEkeywords}
IoT, graphical databases, databases, systems
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2023-10-26 paper.tex
Removed Template Added Citations
Removed all of the template text and added a bibliography file using BibLaTeX

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
+\usepackage{biblatex}
 \usepackage{amsmath,amssymb,amsfonts}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+\addbibresource{citations.bib}
+
 \begin{document}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\printbibliography
 

### 2023-10-27 paper.tex
Added parts to tex and more sources
Added Introduction, Related Works, Methodology, and headers for Results, Analysis, Future Work, and Conclusion. Also added more sources to the citations bib

@@
 \begin{abstract}
-IoT devices have exploded in use over the past few years.
-This has caused concerns over data privacy and security.
+The wide spread proliferation of Internet of Things (IoT) devices
+have brought up many questions and concerns about their security
+and how much data they truly collect.
 Many papers have been writen to detect IoT devices and catalog them,
@@
 \section{Introduction}
+Smart homes are all the rage now adays. There are smart devices everywhere, from lights to door locks.
+It seems that these devices, which are refered to by their collective as Internet of Things or IoT devices, are everywhere.
+With all these new devices come a whole slew of concerns about privacy and security \cite{IoTInspector}.
+There are many papers that explore these concerns, what this paper seeks to explore is how those findings are
+aggregated and stored. There has been a lot of success at using graphical databases due to their speed for querying
+on certain questions regarding big data.
+
+\section{Related Works}
+There are many current systems that implement different components of the general idea of graphical databases for
+IoT device management andanomoly detection, but none put these components together. \textit{IoT Inspector} is a great
+tool that performs the task of monitoring using a form of a relational database, but not a graphical one \cite{IoTInspector}.
+The authors of \textit{The Graph of Things} created such a system for aggregating IoT devices worldwide \cite{GraphofThings}; 
+However, these systems are not built for small networks or home users.
+
+\section{Methodology}
+The first step of the methodology was to determine the technology stack. It was determined that NMap would be used
+to scan for devices, TCPDump would be used for packet capture, Python for programming, and Neo4J for the database
+technology. The database technology was the most difficult to determine due to the unique challenges faced 
+when using a graphical database. The first idea was to use the Resource Description Framework (RDF) as the base.
+There currently does exist an ontology using RDF for IoT devices \cite{RDFIoT}. Indeed, using an ontology for IoT devices
+is very useful for cataloging at scale \cite{IoTSmartOntology}. However, this project is not designed for scale, but for
+the userspace. For this RDF has some drawbacks such as needing a separate node and edge for details about a parent node.
+This is not optimal for both performance and size. It was determined, then, to go with a graphical model that allows
+for information to be included with each node. This is where Neo4J comes in. With attributes being stored in JSON files
+connected to the nodes makes it optimal for this use.
+
+\section{Results}
+
+\section{Analysis}
+
+\section{Future Work}
+
+\section{Conclusion}
 

### 2023-11-26 main.py
Data Import and Tests
Finished Data Import and Began to Implement Tests

@@ -1,7 +1,7 @@
 import csv
 
 import nmap
-from neo4j import GraphDatabase
+from neo4j import GraphDatabase, RoutingControl
 
 # For ARP Spoofing
 # https://www.tutorialspoint.com/python_penetration_testing/python_penetration_testing_arp_spoofing.htm
@@ -15,6 +15,7 @@ class PaperScanner:
 
         self.data = []
 
+        '''
         with open("data/UNSW_2018_IoT_Botnet_Full5pc_1.csv") as csvfile:
             csvreader = csv.DictReader(csvfile)
             for row in csvreader:
@@ -27,9 +28,92 @@ class PaperScanner:
                     "MERGE (:Device {addr: $addr})",
                     addr=row['daddr'],
                     database_='neo4j')
-            print(self.data[0].keys())
-            print(f"{self.data[0]['saddr']} -> {self.data[0]['daddr']}")
-            print((self.data[0]['sport'],self.data[0]['dport'],self.data[0]['proto']))
+
+                self.driver.execute_query(
+                    "MATCH (saddr:Device {addr: $saddr}), (daddr:Device {addr: $daddr}) MERGE (saddr)-[:HasDetails {sport: $sport, dport: $dport, proto: $proto, stime: $stime}]->(daddr)",
+                    saddr=row['saddr'],
+                    daddr=row['daddr'],
+                    sport=row['sport'],
+                    dport=row['dport'],
+                    proto=row['proto'],
+                    stime=row['stime'],
+                    database_='neo4j'
+                )
+        '''
+
+        print()
+        print("===============")
+        print("= Data Parsed =")
+        print("===============")
+        print()
+
+        print("=========================")
+        print("= Executing Query Tests =")
+        print("=========================")
+        print()
+
+        print("===================")
+        print("= Number of Nodes =")
+        print("===================")
+        print()
+
+        node_count, _, _ = self.driver.execute_query(
+                    "MATCH (a:Device) RETURN count(a) AS count",
+                    database_='neo4j', routing_=RoutingControl.READ)
+        
+        print(node_count[0])
+
+        print()
+        print("===========================")
+        print("= Number of Relationships =")
+        print("===========================")
+        print()
+
+        rel_count, _, _ = self.driver.execute_query(
+                    "MATCH (:Device)-[a]->(:Device) RETURN count(a) AS count",
+                    database_='neo4j', routing_=RoutingControl.READ)
+        
+        print(rel_count[0])
+
+        print()
+        print("==========================================")
[…]

### 2023-11-27 main.py
Added additional tests
Added some more tests to get more information out of the data

@@ -1,4 +1,6 @@
 import csv
+import datetime
+import math
 
 import nmap
 from neo4j import GraphDatabase, RoutingControl
@@ -110,10 +112,104 @@ class PaperScanner:
             print(f'{node["a.addr"]} has {to_rels[0]["count"]} incoming relationships')
 
         print()
-        print("=============================================")
-        print("= 3.) How Much Time Passed Between Sessions =")
-        print("=============================================")
+        print("=======================================================")
+        print("= 3.) How many packets are sent per second on average =")
+        print("=======================================================")
         print()
+
+        nodes, _, _ = self.driver.execute_query(
+                    "MATCH (a:Device) RETURN a.addr",
+                    database_='neo4j', routing_=RoutingControl.READ)
+        
+        for node in nodes:
+            to_rels, _, _ = self.driver.execute_query(
+                    "Match (:Device {addr: $addr})-[b]->() RETURN b.stime",
+                    addr=node["a.addr"],
+                    database_='neo4j')
+            
+            packs_per_sec = []
+            curPacks = 0
+            curTime = -1
+            for rel in to_rels:
+                if curTime == -1:
+                    curTime = math.floor(float(rel["b.stime"]))
+
+                if float(rel["b.stime"]) - curTime < 1:
+                    curPacks = curPacks + 1
+                else:
+                    curTime = math.floor(float(rel["b.stime"]))
+                    packs_per_sec.append(curPacks)
+                    curPacks = 0
+
+            if len(packs_per_sec) != 0:
+                avg_packs_per_sec = sum(packs_per_sec) / len(packs_per_sec)
+            else:
+                avg_packs_per_sec = 0.0
+
+
+            print(f'{node["a.addr"]} sends {avg_packs_per_sec} packets per second on average')
+
+        print()
+        print("===========================================================")
+        print("= 4.) How many packets are received per second on average =")
+        print("===========================================================")
+        print()
+
+        nodes, _, _ = self.driver.execute_query(
+                    "MATCH (a:Device) RETURN a.addr",
+                    database_='neo4j', routing_=RoutingControl.READ)
+        
+        for node in nodes:
+            to_rels, _, _ = self.driver.execute_query(
+                    "Match ()-[b]->(:Device {addr: $addr}) RETURN b.stime",
+                    addr=node["a.addr"],
+                    database_='neo4j')
+            
+            packs_per_sec = []
+            curPacks = 0
[…]

### 2023-11-29 paper.tex
Added More Tests, Final
Added More Tests and started the Final Presentation and Paper

--- 2023-10-26 paper.tex
@@
 
-\title{Graphical Databases for IoT Device Management and Anomoly Detection}
+\title{Graph Databases for Use with Timeseries IoT Datasets}
 
@@
 \begin{abstract}
-IoT devices have exploded in use over the past few years.
-This has caused concerns over data privacy and security.
-Many papers have been writen to detect IoT devices and catalog them,
-however none use a graphical database in order to do so.
-Using a graphical database provides many benefits over current systems
-and allows for new questions to be answered.
+The wide spread proliferation of Internet of Things (IoT) devices
+have brought up many questions and concerns about their security
+and what they do with data. Many solutions have appeared using 
+various solutions such as IoT Inspector \cite{IoTInspector}. 
+However, these solutions don't make use of the unique capabilities
+and efficiencies that graph databases provide. This paper seeks
+to use a graph database in order to answer challenging questions 
+about IoT devices particularly within the realm of timeseries datasets.
 \end{abstract}
@@
 \section{Introduction}
+Smart homes are everywhere now adays, from lights to door locks, TVs to speakers.
+It seems that these devices, which are refered to by their collective as Internet of Things or IoT devices, are in every home.
+With all these new devices come a whole slew of concerns about privacy and security \cite{IoTInspector}.
+There are many papers that explore these concerns, what this paper seeks to persue is how to efficiently analyze
+data collected from these devices such that people may infer various aspects about their devices. In particular,
+this paper seeks to see what what info can be garnered from timeseries datasets. Such aspects could include
+anything from what the device is doing to answering if a device is attacking the network and how.
+
+It was decided that using a graph database could provide answers to these questions
+more efficiently and easily than a relational database. The primary advantage for use in this paper
+is the fact that graph databases are great for use with densely connected data \cite{GraphSurvey}.
+On top of this, they are very quick to query and will give a result relatively quickly compared to
+other solutions \cite{GraphSurvey}.
+
+\section{Related Works}
+There are many current systems that implement different components of the general idea of graphical databases for
+IoT device management andanomoly detection, but none put these components together. \textit{IoT Inspector} is a great
+tool that performs the task of monitoring using a form of a relational database, but not a graphical one \cite{IoTInspector}.
+The authors of \textit{The Graph of Things} created such a system for aggregating IoT devices worldwide \cite{GraphofThings}; 
+However, these systems are not built for small networks or home users.
+
+\section{Methodology}
+The first step in this project was choosing the technology that was to be used. It was decided to use Neo4J
+and Python for the tech stack.
+
+\section{Results}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure1.png}
+    \centering
+    \caption{The number of flows that were sent from particular IP addresses}
+    \label{fig:flowfrom}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure2.png}
+    \centering
+    \caption{The number of flows that were sent to particular IP addresses}
+    \label{fig:flowto}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure3.png}
+    \centering
+    \caption{The number of flows that were sent from particular IP addresses per second}
+    \label{fig:sentfrompersec}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure4.png}
+    \centering
+    \caption{The number of flows that were sent to particular IP addresses per second}
+    \label{fig:senttopersec}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure5.png}
+    \centering
+    \caption{The number of ports contacted per IP address}
+    \label{fig:portscontacted}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=8cm]{Figure6.png}
+    \centering
+    \caption{The number of flows from unique IP addresses coming into a particular IP address}
+    \label{fig:incomingflows}
+\end{figure}
+
+\section{Analysis}
+
+\section{Future Work}
+
+\section{Conclusion}
 

### 2023-11-29 main.py

@@ -208,8 +208,29 @@ class PaperScanner:
                 port = rel["b.dport"]
                 ports_count[port] = ports_count.get(port, 0) + 1
 
-            for port in ports_count.keys():
-                print(f'{node["a.addr"]} receives packets through port {port} {ports_count[port]} times')
+            # for port in ports_count.keys():
+            #     print(f'{node["a.addr"]} receives packets through port {port} {ports_count[port]} times')
+
+            print(f'{node["a.addr"]} contacted {len(ports_count)} ports')
+
+        print()
+        print("================================================")
+        print("= 6.) How many incoming flows does a node have =")
+        print("================================================")
+        print()
+
+        nodes, _, _ = self.driver.execute_query(
+                    "MATCH (a:Device) RETURN a.addr",
+                    database_='neo4j', routing_=RoutingControl.READ)
+        
+        for node in nodes:
+            to_rels, _, _ = self.driver.execute_query(
+                    "Match (b:Device)-[]->(:Device {addr: $addr}) RETURN COUNT(DISTINCT b) AS count",
+                    addr=node["a.addr"],
+                    database_='neo4j')
+            
+            for rel in to_rels:
+                print(f'{node["a.addr"]} had {rel["count"]} attempts to connect')
 
 
 class IoTScanner:

### 2023-11-29 paper.tex
Edits to Final Paper
Made many edits to final paper

@@
 On top of this, they are very quick to query and will give a result relatively quickly compared to
-other solutions \cite{GraphSurvey}.
+other solutions \cite{GraphSurvey}. In particular, the use for home users and smaller networks was 
+examined by asking what queries could be run on a smaller dataset as well as what would be reasonable
+for a home user as far as time and efficiency.
 
@@
 The authors of \textit{The Graph of Things} created such a system for aggregating IoT devices worldwide \cite{GraphofThings}; 
-However, these systems are not built for small networks or home users.
+However, these systems are not built for small networks or home users. What this paper seeks to explore is what questions
+can a graph database answer for these smaller networks, home users, and generally users with smaller amounts of
+IP addresses being used. The queries and dataset going forward were chosen with these thoughts in mind.
 
 \section{Methodology}
-The first step in this project was choosing the technology that was to be used. It was decided to use Neo4J
-and Python for the tech stack.
+This projects main goal was to see the about the ease of use for a graph database for answering certain questions.
+It was hypothesied that fairly simple queries to the database would allow the author to gain large amounts of
+information to be analyzed and from which many conclusions could be drawn.
+
+The first towards determining this hypothesis was choosing the technology that was to be used. It was decided 
+to use Neo4J and Python for the tech stack. Neo4J was chosen due to its unique feature of having practically 
+unlimited properties attached to both the nodes and the edges. This was particularly useful when working with 
+5-tuples where the nodes could hold the addresses and the edged could hold the ports, protocals, and a timestamp.
+Python was chosen due to its ease of use, quick prototyping, and library support for Neo4J.
+
+The next step was aquaring the data. In this regard, after a long time of testing and consideration, it was
+determined that using a prebuilt dataset would be the best and most time efficient. A perfect dataset was
+found with BoT IoT \cite{BoTIoT}. This dataset includes both simulated and real world IoT devices as well
+as showing many attacks on these devices. Using such a dataset would allow for getting great amounts of
+patterns for which queries could be written to detect. In addition, being timeseries based, it was perfect
+for this paper.
+
+With both the tech stack and dataset decided, the next step was to decide what types of queries should be
+written to get the most out of the potentials of both the dataset and graph databases as a whole. Some basic
+queries were written with some queries left to future work due to lack of knowledge and time on the part of 
+the author. The basic queries included queries such as flows to and from an IP address to determine whether
+a device was a sink, source, or equal with regards to flow direction, how many flows were sent/received per
+second, how many ports were contacted, and the number of incoming flows to a particular address. These queries
+were chosen in particular to look at two certain attacks: DDoS and Network Scan attacks. If an address were a 
+sink, it could be a target, if it was a source it could be an attacker for DDoS. However to truly determine this
+flows per second and incoming flows would also need to be detected. For Network Scans, if the number of ports
+an IP address sends a flow to is abnormally high, it is a likely indicator that a network scan is being performed.
+
+The last step was writting the program and aquiring the results. This produced some very interesting conclusions
+and was satisfying to the author. This also happened to be the longest part of the methodology as parsing all the
+data took a relatively long time, over a day and a half to parse 1,000,000 flows into the database. Once parsed,
+however, the queries were very quick with the longest taking only a matter of seconds to execute.
 
 \section{Results}
+
+With the experiments done and the data aquired there were some interesing results that were discovered. One such
+discovery was that, within the dataset being used, there were clear sinks and sources for flows as shown in figures
+\ref{fig:flowfrom} and \ref{fig:flowto}.
 
@@
 
+A clear pattern of sending and receiving was being established in the data which is a potential indicator of some
+sort of attack whether DDoS, Network Scanning or otherwise. To determine this further, the average number of flows
+per second was determined as shown in figures \ref{fig:sentfrompersec} and \ref{fig:senttopersec}.
+
 \begin{figure}[h]
@@
 
+As with figures \ref{fig:flowfrom} and \ref{fig:flowto}, these figures also showed clear trends with definitive
+sinks and sources, however this was not enough to fully determine what was going on with this data. To make a more
+definitive conclusion the number of ports each IP address contacted was found as shown in figure \ref{fig:portscontacted}.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+This figure provided a more definitive idea about what was going on for some of the IP Addresses. In particular,
+192.168.100.148 contacted the most ports likely indicating that it was performing a network scan on one of the
+other networks. Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence.
 
@@
 
-\section{Analysis}
+\section{Discussion}
 

### 2023-12-01 paper.tex
Final Paper Close to Finished
The final paper is close to finish

@@
 
+With the question of network scans out of the way, the last question remained.
+Was it possible that any of the sinks were being DDoSed?
+For a DDoS to occur there should be an odd number of incoming, unique, flows to a particular IP address.
+
 \begin{figure}[h]
@@
 
+As shown in figure \ref{fig:incomingflows} there is no evidence that any DDoS attacks occured withing this timeframe,
+ruling out a DDoS attack as a source of the flows to the IoT device.
+
 \section{Discussion}
+
+Clearly the work done here is just the beginning, however the results already gained show great promise of revealing
+important information. From so little data and simple queries we can already determine whether two important attacks
+occur. However the results found by these queries on this dataset are limited. For one, only simple queries were
+and more advanced queries could and should be used in the future in order to solve more complicated problems and
+answer more complicated questions. Secondly, the fraction of the dataset used only involved 1,000,000 flows. In
+order to get a more accurate picture of a network, millions more flows so be gathered and analyzed. Luckily,
+due to the speed of graph databases, this shouldn't be a problem for similar experiments in the future.
 
@@
 
+The work in this paper should be considered a beginning rather than an end. There are so many doors and paths
+the author was not able to take during this project due to various limitations and constraints. Work for both
+the author and readers for the future include, but are not limited to, expanding the queries performed to answer
+more complicated questions. In addition, additional work should be done to analyze these basic questions at scale,
+whether that be scale of time or scale of data. More work also needs to be performed on the comparison of the
+utility of graph databases for these tasks in comparison to more traditional methods as well as the benefits
+and/or downfalls to increasing efficiency of the existing systems for these tasks.
+
 \section{Conclusion}
+Graph databases proved to be a useful tool for IoT device timeseries data. It is both fast to query and the
+information gained provide meaningful answers to interesting questions.
 

### 2023-12-04 paper.tex
More changes to final report
More changes to final report
pushed by nathaniel westlake

@@
 
+The hope of this paper is to find if graph databases are truly a good solution for these users and see
+if they are able to answer questions that these users would want to ask about their networks. For instance,
+we explore finding whether or not certain attacks had taken place on these systems, a question that would
+likely interest anyone running a network of IoT devices.
+
 \section{Related Works}
@@
 discovery was that, within the dataset being used, there were clear sinks and sources for flows as shown in figures
-\ref{fig:flowfrom} and \ref{fig:flowto}.
+\ref{fig:flowfrom} and \ref{fig:flowto}. These were found by writing a query to determine how many relations were 
+being sent both from a node (figure \ref{fig:flowfrom}) and to a node (figure \ref{fig:flowto}).
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure1.png}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure2.png}
@@
 sort of attack whether DDoS, Network Scanning or otherwise. To determine this further, the average number of flows
-per second was determined as shown in figures \ref{fig:sentfrompersec} and \ref{fig:senttopersec}.
+per second was determined as shown in figures \ref{fig:sentfrompersec} and \ref{fig:senttopersec}. This was gained in
+a similar fashion to figure \ref{fig:flowfrom} and \ref{fig:flowto} with dividing them further based on their Unix
+time stamp and making an average.
 
-\begin{figure}[h]
+While it is good to see how much data was being sent overall, it doesn't really tell very much about what's happening.
+In order to determine something like a DDoS attack, the average packets sent pers second was determined to be more useful.
+
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure3.png}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure4.png}
@@
 sinks and sources, however this was not enough to fully determine what was going on with this data. To make a more
-definitive conclusion the number of ports each IP address contacted was found as shown in figure \ref{fig:portscontacted}.
+definitive conclusion the number of ports each IP address contacted was found as shown in figure 
+\ref{fig:portscontacted}. This query was performed by counting the unique ports contacted by each IP address.
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure5.png}
@@
 192.168.100.148 contacted the most ports likely indicating that it was performing a network scan on one of the
-other networks. Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence.
+other networks. Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence. This query
+was performed by looking at the unique nodes that connected to the IP addresses.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \includegraphics[width=8cm]{Figure6.png}
@@
 important information. From so little data and simple queries we can already determine whether two important attacks
-occur. However the results found by these queries on this dataset are limited. For one, only simple queries were
+occur. From data such as flows per second and unique devices connecting it is possible to figure out if a DDoS attack
+is occuring. From data such as ports contacted it is possible to see if the network is being scanned.
+However the results found by these queries on this dataset are limited. For one, only simple queries were
 and more advanced queries could and should be used in the future in order to solve more complicated problems and
@@
 \section{Conclusion}
-Graph databases proved to be a useful tool for IoT device timeseries data. It is both fast to query and the
-information gained provide meaningful answers to interesting questions.
+While there are many avenues this work could take in the future, the goal that this paper set out with was
+achieved. It was shown that graph databases could effectively use IoT timeseries data to answer questions
+that would be of interest to both home and small network users. It has been shown that graph databases work
+on timeseries databases with relatively simple queries to produce results for real world applications
 

### 2023-12-05 paper.tex
Aaaaaaaaaaaaaaaaaah
Aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaah

@@
 
-This figure provided a more definitive idea about what was going on for some of the IP Addresses. In particular,
-192.168.100.148 contacted the most ports likely indicating that it was performing a network scan on one of the
-other networks. Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence. This query
-was performed by looking at the unique nodes that connected to the IP addresses.
+This figure provided a more definitive idea about what was going on for some of the IP Addresses. This query
+was performed by looking at the unique nodes that connected to the IP addresses. In order
+to determine whether a network scan had occured, one must look at the number of ports contacted on a particular
+device within quick succession in a particular timeframe. If it is an abnormally high number, it is likely a 
+network scan attack has occurred. In particular, 192.168.100.148 contacted the most ports at 280 ports total 
+being contacted likely indicating that it was performing a network scan on one of the other networks. 
+Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence at 82 and 127 ports
+contacted respectively.
 
@@
 
-As shown in figure \ref{fig:incomingflows} there is no evidence that any DDoS attacks occured withing this timeframe,
-ruling out a DDoS attack as a source of the flows to the IoT device.
+As shown in figure \ref{fig:incomingflows} there are very few flows to any device. All devices in this sample have 
+only one or two connections. In order to determine if a DDoS attack had occured within a timeframe, what would have
+to be looked for is an abnormally large number of flows coming into a device in order for it to be considered
+distributed. Without it, there is no proper way of determaning Denial of Service from flow data alone. 
+Thus, there is no evidence that any DDoS attacks occured withing this timeframe, ruling out a DDoS attack as a source 
+of the flows to the IoT device.
 

### 2023-12-05 paper.tex
Paper finished?
The paper is finished to a reasonable degree pending further review.

@@
 \begin{IEEEkeywords}
-IoT, graphical databases, databases, systems
+IoT, Graphical Databases, Database Systems, Systems
 \end{IEEEkeywords}
@@
 
-The hope of this paper is to find if graph databases are truly a good solution for these users and see
-if they are able to answer questions that these users would want to ask about their networks. For instance,
-we explore finding whether or not certain attacks had taken place on these systems, a question that would
-likely interest anyone running a network of IoT devices.
+The hope of this paper is to provide basic evidence to determine if graph databases are truly a good solution 
+for these users and see if they are able to answer questions that these users would want to ask about their 
+networks. For instance, we explore finding whether or not certain attacks had taken place on these systems,
+a question that would likely interest anyone running a network of IoT devices. What this paper is not, however,
+is a comprehensive review of this method against all the existing methods out there. While this would be
+undoubtadly useful, due to constraints and limitations faced by the author this has been left up to future work.
 
@@
 It was hypothesied that fairly simple queries to the database would allow the author to gain large amounts of
-information to be analyzed and from which many conclusions could be drawn.
+information to be analyzed and from which many conclusions could be drawn while allowing for efficiency such that
+these tests could be performed on a home computer in a relatively short amount of time.
 
@@
 5-tuples where the nodes could hold the addresses and the edged could hold the ports, protocals, and a timestamp.
-Python was chosen due to its ease of use, quick prototyping, and library support for Neo4J.
+Python was chosen due to its ease of use, quick prototyping, and library support for Neo4J. Both were utilized to
+create a relatively simple program that would analyze the dataset, analyze the data, and return some
+useful results.
 
-The next step was aquaring the data. In this regard, after a long time of testing and consideration, it was
+In regards to the dataset used for this paper, after a long time of testing and consideration, it was
 determined that using a prebuilt dataset would be the best and most time efficient. A perfect dataset was
@@
 patterns for which queries could be written to detect. In addition, being timeseries based, it was perfect
-for this paper.
+for this paper. A subset of this dataset was extracted and used. This subset included a few seconds worth of
+data. From this data, 5-tuples were extracted containing the source address, destination address, source port,
+destination port, and protocol. In addition, the Unix timestamp was extracted for each datapoint to properly
+transfer it as timeseries data.
 
@@
 
-The last step was writting the program and aquiring the results. This produced some very interesting conclusions
-and was satisfying to the author. This also happened to be the longest part of the methodology as parsing all the
-data took a relatively long time, over a day and a half to parse 1,000,000 flows into the database. Once parsed,
-however, the queries were very quick with the longest taking only a matter of seconds to execute.
+The last step in this entire process was writting the program and aquiring the results. This produced some very 
+interesting conclusionsand was satisfying to the author. This also happened to be the longest part of the methodology
+as parsing all thedata took a relatively long time, over a day and a half to parse 1,000,000 flows into the database. 
+Once parsed, however, the queries were very quick with the longest taking only a matter of seconds to execute. This
+helped to support the hypothesis of it being efficient to run on a home computer while hurting the results with the
+amount of time it took to parse the data. Future research should be performed to determine whether using live
+timeseries data would make this process more or less efficient.
 
@@
 
-A clear pattern of sending and receiving was being established in the data which is a potential indicator of some
-sort of attack whether DDoS, Network Scanning or otherwise. To determine this further, the average number of flows
-per second was determined as shown in figures \ref{fig:sentfrompersec} and \ref{fig:senttopersec}. This was gained in
-a similar fashion to figure \ref{fig:flowfrom} and \ref{fig:flowto} with dividing them further based on their Unix
-time stamp and making an average.
+A clear pattern of sending and receiving was being established in the data. The IP addresses that were sinks had hundreds of thousands
+of flows going into them whereas the sources had 285 at the highest. If one were to look at the flows coming out the
+relationship is opposite. These features could be potential indicators of some sort of attack whether DDoS,
+Network Scanning or otherwise. To determine this further, the average number of flows per second was determined as
+shown in figures \ref{fig:sentfrompersec} and \ref{fig:senttopersec}. This was gained in a similar fashion to figure 
+\ref{fig:flowfrom} and \ref{fig:flowto} with dividing them further based on their Unix time stamp and making an average.
 
@@
 As with figures \ref{fig:flowfrom} and \ref{fig:flowto}, these figures also showed clear trends with definitive
-sinks and sources, however this was not enough to fully determine what was going on with this data. To make a more
-definitive conclusion the number of ports each IP address contacted was found as shown in figure 
-\ref{fig:portscontacted}. This query was performed by counting the unique ports contacted by each IP address.
+sinks and sources. Like before, the sinks have hundreds of thousands of flows received per second whereas the sources
+send hundreds of thousands of flows per second. However this was not enough to fully determine what was going on with
+this data. To make a more definitive conclusion the number of ports each IP address contacted was found as shown in 
+figure \ref{fig:portscontacted}.
 
@@
 This figure provided a more definitive idea about what was going on for some of the IP Addresses. This query
-was performed by looking at the unique nodes that connected to the IP addresses. In order
+ was performed by counting the unique ports contacted by each IP address. In order
 to determine whether a network scan had occured, one must look at the number of ports contacted on a particular
@@
 
-As shown in figure \ref{fig:incomingflows} there are very few flows to any device. All devices in this sample have 
+As shown in figure \ref{fig:incomingflows} there are very few flows to any device. This query
+was performed by looking at the unique nodes that connected to the IP addresses. All devices in this sample have 
 only one or two connections. In order to determine if a DDoS attack had occured within a timeframe, what would have
@@
 
-\section{Discussion}
+\section{Discussion and Future Work}
 
 Clearly the work done here is just the beginning, however the results already gained show great promise of revealing
-important information. From so little data and simple queries we can already determine whether two important attacks
-occur. From data such as flows per second and unique devices connecting it is possible to figure out if a DDoS attack
-is occuring. From data such as ports contacted it is possible to see if the network is being scanned.
-However the results found by these queries on this dataset are limited. For one, only simple queries were
-and more advanced queries could and should be used in the future in order to solve more complicated problems and
-answer more complicated questions. Secondly, the fraction of the dataset used only involved 1,000,000 flows. In
-order to get a more accurate picture of a network, millions more flows so be gathered and analyzed. Luckily,
-due to the speed of graph databases, this shouldn't be a problem for similar experiments in the future.
+important information. From so little data and simple queries we can already get a good idea about whether two 
+important attacks occur in a matter of seconds. From data such as flows per second and unique devices connecting it is possible to figure 
+out if a DDoS attack is occuring. From data such as ports contacted it is possible to see if the network is being
+scanned. The results thus far are promising about a future for this project, however the results found by these
+queries on this dataset are limited. For one, only simple queries were and more advanced queries could and should 
+be used in the future in order to solve more complicated problems and answer more complicated questions. Secondly, 
+the fraction of the dataset used only involved 1,000,000 flows. In order to get a more accurate picture of a network, 
+millions more flows so be gathered and analyzed. Luckily, due to the speed of graph databases, this shouldn't be a 
+problem for similar experiments in the future. There are so many doors and paths the author was not able to take 
+during this project due to various limitations and constraints.
 
-\section{Future Work}
+Expanding the queries performed to answer more complicated questions was one such work that the author was not able 
+to conduct during the writing of this paper. However, such work would be very useful in order to gain more analytics
+to answer questions including, but certainly not limited to, detecting patterns in the flows where it is seen how 
+often flows are sent and if they appear targeted more to one device rather than another.
 
-The work in this paper should be considered a beginning rather than an end. There are so many doors and paths
-the author was not able to take during this project due to various limitations and constraints. Work for both
-the author and readers for the future include, but are not limited to, expanding the queries performed to answer
-more complicated questions. In addition, additional work should be done to analyze these basic questions at scale,
-whether that be scale of time or scale of data. More work also needs to be performed on the comparison of the
-utility of graph databases for these tasks in comparison to more traditional methods as well as the benefits
-and/or downfalls to increasing efficiency of the existing systems for these tasks.
+Additional work should be done to analyze these basic questions at scale, whether that be scale of time or scale of 
+data. The very small sample of data only encompased a few seconds of flow traffic with only six IP Addresses being
+monitored. For a true, real-world test of this system, timeseries data spanning minutes, hours, or even days should 
+be used. In addition, a more fleshed out, small network testbed should be used with a greater sample of IoT devices. 
+There are many limitations and challanges on this especially with the papers stated goal of being useful for homes and
+small networks. Such limitations and challanges revolve around the processing power and storage space required to
+analyze and store such data. However, that is precicely what makes this an optimal work to determine better the 
+feasability of using such systems on home and small networks.
+
+To add onto this, more work also needs to be performed on the comparison of the utility of graph databases for these 
+tasks in comparison to more traditional methods as well as the benefits and/or downfalls to increasing efficiency of 
+the existing systems for these tasks. Due to limitations and constraints involved with this project, very little
+benchmarking was performed, especially as it pertains to comparisons towards relational database management systems.
+Future work should be focused on this topic so as to obtain definitive data comparing the two options as well as what
+relational database systems truly do better or worse on in comparison to graph database systems with regards to
+the specific questions related to IoT timeseries data.
 
@@
 that would be of interest to both home and small network users. It has been shown that graph databases work
-on timeseries databases with relatively simple queries to produce results for real world applications
+on timeseries databases with relatively simple queries to produce results for real world applications such
+as determining attacks on certain devices within a network. The future work mentioned before is both proper
+and necessary for taking this project forward. It is the hope of the author the the findings and questions
+found in this paper prove of use to future research and future projects and that the findings, whatever they
+may be, lead to more efficient use of timeseries data for IoT devices.
 

### 2023-12-05 main.py
Cleanup Main.py
Cleaned up main.py

@@ -1,15 +1,8 @@
 import csv
-import datetime
 import math
 
-import nmap
 from neo4j import GraphDatabase, RoutingControl
 
-# For ARP Spoofing
-# https://www.tutorialspoint.com/python_penetration_testing/python_penetration_testing_arp_spoofing.htm
-import socket
-import struct
-import binascii
 
 class PaperScanner:
     def __init__(self, uri, user, password, eth: str = 'eth0', subnet: str = '10.0.0.0'):
@@ -17,7 +10,6 @@ class PaperScanner:
 
         self.data = []
 
-        '''
         with open("data/UNSW_2018_IoT_Botnet_Full5pc_1.csv") as csvfile:
             csvreader = csv.DictReader(csvfile)
             for row in csvreader:
@@ -41,7 +33,6 @@ class PaperScanner:
                     stime=row['stime'],
                     database_='neo4j'
                 )
-        '''
 
         print()
         print("===============")
@@ -233,38 +224,5 @@ class PaperScanner:
                 print(f'{node["a.addr"]} had {rel["count"]} attempts to connect')
 
 
-class IoTScanner:
-    def __init__(self, uri, user, password, eth: str = 'eth0', subnet: str = '10.0.0.0'):
-        self.nm = nmap.PortScanner()
-        self.nm.scan(subnet + '/24', arguments='-O', sudo=True)
-
-        self.driver = GraphDatabase.driver(uri, auth=(user, password))
-
-        self.sock = socket.socket(socket.AF_INET, socket.SOCK_RAW, socket.htons(0x0800))
-        self.sock.bind((eth, socket.htons(0x0800)))
-
-    def close(self):
-        self.driver.close()
-
-    def init_graph(self):
-        with self.driver.session() as session:
-            for h in self.nm.all_hosts():
-                if 'mac' in iots.nm[h]['addresses']:
-                    device = session.execute_write(self._create_and_return_device, self.nm[h]['addresses']['mac'], self.nm[h]['vendor'])
-
-    @staticmethod
-    def _create_and_return_device(tx, mac, vendor):
-        result = tx.run("CREATE (a:Device) "
-                        "SET a.mac = $mac "
-                        "SET a.vendor = $vendor "
-                        "RETURN a.mac + ' is from vendor ' + a.vendor", mac=mac, vendor=vendor)
-        return result.single()[0]
-
-
 if __name__ == '__main__':
-    '''
[…]
